Environmental behaviour & practices

### 2021-01-15 01-Sustainable-indicators.Rmd
correcting the biblio

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 01-Sustainable-indicators.bib
bibliography: library.bib
nocite: '@*'
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: 01-Sustainable-indicators.bib
bibliography: library.bib
#nocite: '@*'
editor_options: 
  chunk_output_type: console
---

### 2021-01-15 03-comportements.Rmd
correcting the biblio

---
title: "Environmental behaviour & practices"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 03-comportement.bib
nocite: '@*'

@@

---
```{r}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
```

@@

```{r}
TPB <- 
tribble(
  ~Variable, ~Definition, ~Definition.recycling,
  "Attitude", 
    "Attitude toward the behavior and refers to the degree to which a person has a favorable or unfavorable evaluation or appraisal of the behavior in question",
      "The extent to which plastic recycling is valued by people, whether positive or negative",

@@

```{r, include=TRUE}

>>>>

---
title: "Environmental behaviour & practices"
description: |
  some
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 03-comportement.bib
#nocite: '@*'

@@

---
```{r, include=FALSE}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
```

@@

```{r, include=FALSE}
TPB <- 
tribble(
  ~Variable, ~Definition, ~Definition.recycling,
  "Attitude", 
    "Attitude toward the behavior and refers to the degree to which a person has a favorable or unfavorable evaluation or appraisal of the behavior in question",
      "The extent to which plastic recycling is valued by people, whether positive or negative",

@@
